### 2023-03-31 reachable-resilience.tex
Addind huyphothesis on safe and bad in theorems in Sect 4.1

As in the Section~3, we study decidability results for different pairs of sets $\Safe$ and $\Bad$ downard closed and upward closed.

\mathieu{Ici on s'intéresse seulement aux cas $\uparrow \downarrow$ et $\downarrow \uparrow$.}

@@

\begin{theorem}\cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}\label{ref ozkan}
{\sc bounded-state-resilience} and {\sc $k$-state-resilience} are decidable for WSTS $S$ with strong upward compatibility and such that $\uparrow \post^*(s)$ is computable for $s \in S$.
\end{theorem}

@@

\begin{corollary}\label{postcomputable}
{\sc state-resilience} is decidable for WSTS with strong upward compatibility and such that $\uparrow \post^*(s)$ is computable for $s \in S$.
\end{corollary}

@@

\begin{theorem}\label{srp up down}
{\sc State-resilience} is undecidable for strongly compatible WSTS with effective pred-basis.
\end{theorem}

@@

\begin{corollary}\label{bsrp up down}
Bounded state-resilience and 
$k$ state-resilience are undecidable for strongly compatible WSTS with effective pred-basis.
\end{corollary}

@@

\begin{theorem}{(Adjusting Theorem 1 from \cite{DBLP:journals/corr/abs-2108-00889})}\label{post srp}
{\sc Reachable-resilience} is decidable for (not necessarily strong) WSTS with effective 
$\uparrow$ $\post^*$ basis.
\end{theorem}

@@

Undecidability in general: $\Safe = 0$, $\Bad = S \setminus 0$ ?

>>>>

As in the Section~3, we study decidability results for different pairs of sets $\Safe$ and $\Bad$ downard closed and upward closed. We will consider here the cases where 
$\Safe = \uparrow \Safe$ and $\Bad = \downarrow \Bad$ 
and where 
$\Safe = \downarrow \Safe$ and $\Bad = \uparrow \Bad$.

% \mathieu{Ici on s'intéresse seulement aux cas $\uparrow \downarrow$ et $\downarrow \uparrow$.}

@@

\begin{theorem}\cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}\label{ref ozkan}
{\sc bounded-state-resilience} and {\sc $k$-state-resilience} are decidable for WSTS $S$ with strong upward compatibility and such that $\uparrow \post^*(s)$ is computable for $s \in S$
when
$\Safe=\uparrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{theorem}

@@

\begin{corollary}\label{postcomputable}
{\sc state-resilience} is decidable for WSTS with strong upward compatibility and such that $\uparrow \post^*(s)$ is computable for $s \in S$
when
$\Safe=\uparrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{corollary}

@@

\begin{theorem}\label{srp up down}
{\sc State-resilience} is undecidable for strongly compatible WSTS with effective pred-basis
when
$\Safe=\uparrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{theorem}

@@

\begin{corollary}\label{bsrp up down}
Bounded state-resilience and 
$k$ state-resilience are undecidable for strongly compatible WSTS with effective pred-basis
when
$\Safe=\uparrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{corollary}

@@

\begin{theorem}{(Adjusting Theorem 1 from \cite{DBLP:journals/corr/abs-2108-00889})}\label{post srp}
{\sc Reachable-resilience} is decidable for (not necessarily strong) WSTS with effective 
$\uparrow$ $\post^*$ basis
when
$\Safe=\uparrow \Safe$
and $\Bad=\downarrow \Bad$.
\end{theorem}

@@

The problem is however unfortunately undecidable in general.

\begin{theorem}
The resilience problem is undecidable for effective WSTS with  strong  compatibility 
when
$\Safe=\downarrow \Safe$
and $\Bad=\uparrow \Bad$.
\end{theorem}

\begin{proof}
Taking $\Safe = 0$, $\Bad = S \setminus 0$, it follows the state resilience problem is equivalent
to reachability of $0$.
\end{proof}
